The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-11 article.tex
Updated the conclusions (closes #12)

Over the past years since the last CDK publication in 2006, a lot has changed. The functionality
has seen many additions, and the stability of the development model has significantly improved.
This paper outlines how peer review and quality control contributed to a much wider adoption
of our cheminformatics library and seen many new additions. With 93 contributors,
the CDK is alive and kicking.

However, there are many unsolved issues. Performance is perhaps one of the most important ones.
The disadvantage of having an API that supports many data models, is that the API is heavy and
the interface implementations hard to optimize.

>>>>

Since the last CDK publication in 2006, the library has been improved in many
aspects. The functionality has seen many additions and rewrites, making the
library more functional and a lot more faster then before. Updates on the common
SMILES and MDL molfile formats and the improved structure diagram generation are
very visible and benefit many of the tools using the CDK.
Furthermore, the stability of the development model has significantly improved,
providing greater stability of the library over time. The project adopted peer
review and quality control.

With 93 contributors, a long list of tools based on the CDK, and hundreds
of article citations, the CDK is alive and kicking.
